---
title: "My submission"
output: html_document
---

This is work work this this assignment

### Loading and preprocessing the data

This step requires to have activity.csv in the repository
```{r}
data <- read.csv("activity.csv")
data$date<-as.Date(data$date)
```

### What is mean total number of steps taken per day?
```{r}
stepsPerDay <- tapply(data$steps, data$date, sum, na.rm=T)
hist(stepsPerDay, main = "Total number of steps per day", 
    xlab = "Steps per day", ylab = "Frequency")
```

Let's print the mean and the median
```{r}
mean(stepsPerDay, na.rm = T)
median(stepsPerDay, na.rm = T)
```

### What is the average daily activity pattern?
```{r}
steptsPerIntervals <- tapply(data$steps, data$interval, mean, na.rm=T)
hist(steptsPerIntervals, main = "averaged number of steps per interval", 
    xlab = "Steps per interval", ylab = "Frequency")
intervals <- unique(data$interval)
plot(intervals, steptsPerIntervals, type = "l", main = "time series plot of the 5-minute interval",  xlab = "interval", ylab = "Steps per interval")
```

Let's get the interval containing the maximum number of steps
```{r}
intervals[steptsPerIntervals == max(steptsPerIntervals)][1]
```

### Imputing missing values

Lets's print the number of NAs
```{r}
naSteps <- data$steps[is.na(data$steps)]
length(naSteps)
```

I decided to fill missing values with the mean of each step and create my data
```{r}
naSteps <- rep(mean(data$steps, na.rm = T), length(naSteps))
newData <- data[,c(1,2,3)]
newData$steps[is.na(data$steps)] <- naSteps
```

Let's create our new histogram and compute the mean and the median of total number of steps taken per day
```{r}
newStepsPerDay <- tapply(newData$steps, newData$date, sum)
hist(newStepsPerDay, main = "histogram of the total number of steps taken each day")
newStepsPerIntervals <- tapply(newData$steps, newData$interval, mean)
mean(newStepsPerDay)
median(newStepsPerDay)
```
These values differ from the previous ones and the mean is equal to the median (I can't explain that..)

### Are there differences in activity patterns between weekdays and weekends?
```{r}
Sys.setlocale("LC_TIME", "English")
weekends <- c("Saturday", "Sunday")
newData$weekdays <- weekdays(newData$date)
newData$weekdays <- ifelse(newData$weekdays %in% weekends,"weekend","weekday")
newData$weekdays <- as.factor(newData$weekdays)
weekendIndex <- newData$weekdays == "weekend"
newStepsPerIntervalsWeekend <- tapply(newData$steps[weekendIndex], newData$interval[weekendIndex], mean)
newStepsPerIntervalsWeekday <- tapply(newData$steps[!weekendIndex], newData$interval[!weekendIndex], mean)
par(mfrow = c(2,1))
plot(intervals, newStepsPerIntervalsWeekend, type = "l", xlab = "Interval", 
    ylab = "Number of steps", , main = "Weekend")
plot(intervals, newStepsPerIntervalsWeekday, type = "l", xlab = "Interval", 
    ylab = "Number of steps", , main = "Weekday")
```

Between these two patterns the user is walking more in the intervals 500-1000 on weekdays and walking more on 800-2000 intervals